---

title: "My dynamic report"

subtitle: "Analysis of Student Piercings"

output: html_fragment

author: "Angelina Yu"

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

body {background-color: pink}

h2{color:yellow; font-style:italic}

```

## What's going on with this data?

This report is based on the analysis of student piercing data collected through Google Forms. The data mainly includes the following:
Number of piercings: The number of piercings the student has (1-10).
Piercing Type: Describes the type of piercings the student has.
Whether to continue piercing: Reflects whether the student intends to continue piercing in the future.
---

```{r load-data, echo=FALSE}
library(tidyverse)

# Add the URL I posted online to R
csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTSVQ36bjtTRREGNAhaIoijwxh-Ydm-62RtV-9yCpPRIjFPA4hMURndGHAaHOzhFezGy54v8LjJKaPV/pub?output=csv"

#Read data into logged-data
logged_data <- read_csv(csv_url)

latest_data <- logged_data %>%
      rename(
        observationtime = "observationtime",
      numPiercings = "how many piercings do you have?\nuse the number 1-10",
      typePiercings = "what type of piercings do you have?",
      willContinue = "Will you continue to get piercings?")

#find the min, max and mean of number of piercings.
min_piercings <- min(latest_data$numPiercings)
max_piercings <- max(latest_data$numPiercings)
mean_piercings <- mean(latest_data$numPiercings)


#bar charts shows the frequency of different types of piercings
ggplot(latest_data, aes(x = typePiercings))+
  geom_bar(fill="pink", width = 0.6)+
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# bar chart shows the proporttion of whether to continue piercing.
ggplot(latest_data,aes(x = willContinue)) +
  geom_bar(fill = "blue", width = 0.6) +
labs(title = "continue with the idea of pirercing", x = "will continue", y = "count")

```


`r min_piercings` is the minimum piercings.

`r max_piercings` is the maximum piercings.

`r mean_piercings` is the aveage piercings.


Summary
Through the above analysis, we have gained a preliminary understanding of the basic situation of current student piercing data and their future intentions. We use ggplot to display our data more intuitively, and we will continue to pay attention to recording and collecting data.



